On the Functionality of the Multilayer Perceptron

### 2020-09-12 Thesis/Sections/FeatureSelections.tex
Reraan Classifier, Updated Features

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics. In the following sections, we outline the set of $24$ features used in the classification process

@@

\paragraph*{}The $24$ features are from each file are organized into one of two array structures. each called a \textit{design matrix}. A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times p)}
\end{equation}
Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect. (\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}). A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample. Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.

@@

\paragraph*{}From time space, we use the following $10$ features:

@@

\item[•] Waveform Mean, Median, and Mode

@@

\subsubsection{Statistical Distribution Data}
\textcolor{red}{Honetly, I may remove these from the classifier}

>>>>

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics. In the following sections, we outline the set of $21$ features used in the classification process

@@

\paragraph*{}The $21$ features are from each file are organized into one of two array structures. each called a \textit{design matrix}. A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times p)}
\end{equation}
Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect. (\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}). A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample. Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.

@@

\paragraph*{}From time space, we use the following $7$ features:

@@

@@
